\documentclass[../main.tex]{subfile}
\begin{document}

\section{Bogoliubov-de Gennes Formalism} \label{sec:BdGFormalism}
The Bogoliubov-de Gennes transformation allows us to express the Hamiltonian in a diagonal way and express our quantities 
by looking at the eigenvectors of the Hamiltonian. The resulting matrix is expressed in a huge space and is very sparse.\\

To give a taste of it, it will allow us to rewrite our Hamiltonian as following
\begin{align}
    H = E_0 - \frac{1}{2} \check{c}^\dagger \check{H} \check{c}, \label{eq:BdG_intro_H}
\end{align}
involving $\check{c} = (\hat{c}_1,..,\hat{c}_N)$, where each $\hat{c}_i$ is a
 vector containing the creation and annihilation operators of a lattice site $i$:
$\hat{c}_i = (c_{i\uparrow} ,c_{i\downarrow}, c_{i\uparrow}^{\dagger} ,c_{i\downarrow}^{\dagger})$.\\

As we see we just describe each site with the four possible $c$-operators. This means for each lattice site,
we have a $4\times4$-submatrix that reflects the possible combinations of creation and annihilation operators of both spins. 
For the readability we are going to drop the comma between the site and spin indices.\\
For example if one has (without loss of generality) a chemical potential at the site $i$, 
 then the Hamiltonian is described in the following way:
\[
    H_{\mu i} = -\sum_{\sigma} \mu_i c_{i\sigma}^{\dagger} c_{i\sigma}.
\]
If we want to describe it in therm of $\hat{c}_i$ we have:
\[
    H_{\mu,i} = \begin{pmatrix}
        c_{i\uparrow}^{\dagger} \\c_{i\downarrow}^{\dagger}\\ c_{i\uparrow} \\c_{i\downarrow}\\
    \end{pmatrix}\cdot \mu_i
     \begin{pmatrix}
        1 & 0 & 0 & 0\\
        0 & 1 & 0 & 0\\
        0 & 0 & 0 & 0\\
        0 & 0 & 0 & 0
    \end{pmatrix}\begin{pmatrix}c_{i\uparrow} ,c_{i\downarrow}, c_{i\uparrow}^{\dagger} ,c_{i\downarrow}^{\dagger}\end{pmatrix}
\]
Please note that in later discussions we will see the matrix must exhibit a certain symmetry to respect the fermionic relations and have 
real eigenvalues. This was just an example.\\

Depending on the interaction we wish to describe, we can figure out what combination of operators we want and design the $4\times4$ matrix accordingly.
To achieve a full description of the system we can consider the interaction between two site $i,j$ as a $4\times4$ matrix involving the $\hat{c}_i^{\dagger}$ and $c_j$ operators.
Then we can build a huge matrix $\check{H}$ based on $4\times4$ matrices at $\check{H}_{ij}$. The vectors we multiply this matrix with are just the $\hat{c}_i^{\dagger}$ and $c_j$ operators 
stack above one and other forming the above-introduced $\check{c}$ vector. As a result, one gets the first formula introduced in this section at Eq.\ref{eq:BdG_intro_H}.
We can then compute the eigenvalues and -vectors to express the quantities we're interested in. This is what we call the Bogoliubov-de Gennes transformation.\\

Now that the motivation is clear, we need to bring our Hamiltonian in a form that involves the fermionic operators $c_{i\sigma}$ and $c_{i\sigma}^{\dagger}$. 
This section follows closely the derivation of J. A. Ouassou in Ref. \cite{Ouassou_unpubl}. Some details of this derivation are also found in Ref.\cite{Ouassou2024}.
 
\subsection{Tight Binding Model}
Our goal is now to fix our particles on lattice sites and describe their interactions. We are therefore going to translate our wave function formalism in an on-site plus
nearest neighbour description.\\

For the generalities, we assume we have the Hamiltonian in the second quantization formalism:
\begin{align*}
    H = & \sum_{\sigma\sigma'} \int \phi_{\sigma}^{\dagger}(\bm{r}) H_{\sigma\sigma'}(\bm{r}) \psi_{\sigma'}(\bm{r}) \dd^3r\\
    + & \sum_{\sigma\sigma'} \int \int \phi_{\sigma}^{\dagger}(\bm{r})\phi_{\sigma'}^{\dagger}(\bm{r}') V_{\sigma\sigma'}(\bm{r},\bm{r}')
     \phi_{\sigma'}(\bm{r}')\phi_{\sigma}(\bm{r}) \dd^3r'\dd^3r.
\end{align*}
We introduce a basis of so called Wannier orbitals $w(\bm{r} - \bm{R}_i)$ with $\bm{R}_i$ an atom location. There are a multiple way to define these orbitals \cite{Marzari},
but the most simple ones \cite{Wannier1937} is enough here. These describe where the electrons evolve around the atoms and should be large
 in the neighbourhood of $\bm{R}_i$ and vanishes when the distance tends to infinity.
They are therefore called ``localized''. The orbital can build a complete basis and verify the orthonormality condition:
\[
    \int w^{\ast}(\bm{r} - \bm{R}_i) w(\bm{r} - \bm{R}_j) \dd^3r = \delta_{ij}.
\]
From this property we can define some field operators in this basis, based on creation and annihilation operators acting on a lattice site $i$:
\begin{equation}\label{eq:Wannier_fieldOp}
    \phi_{\sigma}(\bm{r}) := \sum_{i} w(\bm{r} - \bm{R}_i) c_{i\sigma} ~,~~~~~ \phi_{\sigma}^{\dagger}(\bm{r}) := \sum_{i} w^{\ast}(\bm{r} - \bm{R}_i) c_{i\sigma}^{\dagger}
\end{equation}
which is not a continuous description any more. 
Inserting these operators back into our above Hamiltonian and using the orthonormality allows us to have an on site/nearest neighbour description of the Hamiltonian. Taking for
instance the first part of the Hamiltonian, we have:
\begin{align*}
    H = & \sum_{\sigma\sigma'} \int \psi_{\sigma}^{\dagger}(\bm{r}) H_{\sigma\sigma'}(\bm{r}) \psi_{\sigma'}(\bm{r}) \dd^3r\\
    =& \sum_{ij\sigma\sigma'} c_{i\sigma}^{\dagger} c_{j\sigma'}\int w^{\ast}(\bm{r} - \bm{R}_i) H_{\sigma\sigma'}(\bm{r}) w(\bm{r} - \bm{R}_j) \dd^3r\\
    := & \sum_{i\sigma\sigma'} \epsilon_i^{\sigma\sigma'} c_{i\sigma}^{\dagger} c_{i\sigma'} - \sum_{\langle ij\rangle\sigma\sigma'} t_{ij}^{\sigma\sigma'} c_{i\sigma}^{\dagger} c_{j\sigma'} + ..   
\end{align*}
In the last line we include a local energy term $\epsilon$ and the so-called hopping term $t_{ij}$, which is the interaction with the nearest neighbour sites $j$ of $i$.
For a more precise description one could consider more neighbour. The spin dependent term can be used to describe spin orbit coupling or spin-flip processes.\\

We now aim to define the useful processes for this thesis using this formalism.

\subsubsection{Non-interacting electrons}
The two main components of the non-interacting system Hamiltonian $H_N$ are the chemical potential $\mu_i$ which is specific to each site and the hopping term $t_{ij}$.
The chemical potential is modulated by the number of particles on the site $i$ and the hopping term gives the amplitudes of moving an electron from site $i$ to $j$.
We assume it as spin-independent here.\\
\begin{equation}\label{eq:Ham_Normal}
    H_N = - \sum_{i \sigma} \mu_i c_{i\sigma}^{\dagger} c_{i\sigma} - \sum_{\langle ij\rangle \sigma} t_{ij} c_{i\sigma}^{\dagger} c_{j\sigma},
\end{equation}
where $\langle ij\rangle$ is a commonly used notation to sum over $i$ and its nearest neighbours $j$, skipping $i=j$. We label it the normal
Hamiltonian.\\

The hopping amplitude can be computed from the overlap of the orbitals under a kinetic operator $-\nabla^2/(2m)$, which explains the meaning ``hopping'':
\begin{align*}
    t_{ij} =& -\int w^{\ast}(\bm{r} - \bm{R}_i) \frac{\nabla^2}{2m} w(\bm{r} - \bm{R}_j) \dd^3r\\
           =& +\frac{1}{2m}\int \left(\nabla w(\bm{r} - \bm{R}_i)\right)^{\ast} \left(\nabla w(\bm{r} - \bm{R}_j)\right) \dd^3r.
\end{align*}
We used a partial integration considering the boundary conditions of the Wannier orbitals $w(\pm \infty) = 0$. Therefore, one part of the partial integration vanishes,
and we integrate/differentiate the integrands in the other integral, leading to two $\nabla$s. Further we see that $t_{ij} = t_{ji}^{\ast}$ by swapping the two integrands.\\

\subsubsection{Superconductivity}
Previous study of ours on the superconductivity have led us to the following Hamiltonian:
\[
    H_S = - \int U(\bm{r}) \psi_{\downarrow}^{\dagger}(\bm{r})\psi_{\uparrow}^{\dagger}(\bm{r})\psi_{\uparrow}(\bm{r})\psi_{\downarrow}(\bm{r}) \dd^3r
\]
on which we can apply a mean field approximation $\Delta(\bm{r}) = U(\bm{r})\langle \psi_{\uparrow}(\bm{r})\psi_{\downarrow}(\bm{r})\rangle$.
This yields to a common BCS-Hamiltonian for regular superconductors.\\
\[
    H_S = - \int \biggl(\Delta(\bm{r}) \psi_{\downarrow}^{\dagger}(\bm{r})\psi_{\uparrow}^{\dagger}(\bm{r}) +
     \Delta(\bm{r})^{\ast}\psi_{\uparrow}(\bm{r})\psi_{\downarrow}(\bm{r})\biggr) \dd^3r.
\]  
We see that we the second integrand is just the complex conjugate of the first one. 
To spare some place, we are going to focus ourselves on the first one and denoted its homologue with $h.c.$ ``hermitian conjugate''. We insert Eq.$\ref{eq:Wannier_fieldOp}$ 
in our last expression and obtain:
\begin{align*}
    H_S =& - \sum_{ij} c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger} \int \Delta(\bm{r}) w^{\ast}(\bm{r} - \bm{R}_i) w^{\ast}(\bm{r} - \bm{R}_j) \dd^3r + \text{h.c.}\\
    :=& -\sum_{ij} \Delta_{ij} c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger} + \text{h.c.}
\end{align*}
Let's talk the coherence length of the Cooper pairs. Its is antiproportional to the gap $\Delta$ and gives the extent of the correlation of the operators $c_{i\uparrow}$ and $c_{j\downarrow}$.
$\Delta(\bm{r})$ is an order parameter and doesn't vary much in the coherence length, which is much bigger than the atomic length.
Therefore, we can say that the orbitals vary faster than the gap \cite{Jabir2021}. Moreover, these orbitals are picked in the neighbourhood of the atomic location $\bm{R}_i$ and $\bm{R}_j$.
Achieving the integral we get $\Delta_{ij} = \Delta_i \delta_{ij}$. We can from then reintroduce the h.c. and we get:
\begin{equation}\label{eq:Ham_Superc    ond_Tight}
    H_S = -\sum_{i} \Delta_i c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger} + \Delta_i^{\ast} c_{i\uparrow}c_{i\downarrow}.
\end{equation}
We're however missing the mean field term $E_0$:
\[
    E_0 = \int U \langle \psi_{\downarrow}^{\dagger}\psi_{\uparrow}^{\dagger}\rangle \langle\psi_{\uparrow}\psi_{\downarrow}\rangle \dd^3r 
    = \int U \frac{\Delta^{\ast}}{U}\frac{\Delta}{U} \dd^3r = \int \frac{|\Delta|^2}{U} \dd^3r.
\]
After applying the tight binding formalism we get:
\[
    E_0 = \sum_{i} \frac{|\Delta_i|^2}{U},
\]
which is a term we can add to the Hamiltonian in Eq.\ref{eq:Ham_Supercond_Tight}. Form these equations we have the final 
Hamiltonian for the superconducting system:
\[
    H = E_0 + H_N + H_S.
\]  
\subsection{A more symmetric Hamiltonian}
As we introduced it while motivating the Bogoliubov-de Gennes formalism, we aspire to describe each state as a vector-matrix-vector product of
\[
    \hat{c}_i = \left(c_{i\uparrow}, c_{i\downarrow},c_{i\uparrow}^{\dagger}, c_{i\downarrow}^{\dagger}\right).
\]
However, using the form we have in the superconducting (Eq.\ref{eq:Ham_Supercond_Tight}) and normal (Eq.\ref{eq:Ham_Normal}) 
Hamiltonian will later not act as a fermionic operator upon the transformation we're about to
do. We need to rewrite the Hamiltonian in a more symmetric way to later respect the anticommutation relations.\\

\paragraph{The chemical potential} It can be expressed using the anticommutation relations of the fermionic operators $[c_{i\sigma}^{\dagger},c_{i\sigma}]_+ = 1$:
\begin{equation}\label{eq:SymHam_muTerm}
    \sum_{i\sigma} \mu_i c_{i\sigma}^{\dagger} c_{i\sigma} = \frac{1}{2}\sum_{i\sigma} \mu_i \left(c_{i\sigma}^{\dagger}c_{i\sigma} - c_{i\sigma}c_{i\sigma}^{\dagger} + 1\right)
\end{equation}
The trick we used is quite straight forward but not obvious. Taking two different states $\alpha$ and $\gamma$ we have:
\[
    c^{\dagger}_{\alpha}c_{\gamma} ~=~ \frac{1}{2}c^{\dagger}_{\alpha}c_{\gamma} + \frac{1}{2}c^{\dagger}_{\alpha}c_{\gamma} ~=~ \frac{1}{2}c^{\dagger}_{\alpha}c_{\gamma} + \underbrace{\frac{1}{2}c^{\dagger}_{\alpha}c_{\gamma} + \frac{1}{2}c_{\gamma}c^{\dagger}_{\alpha}}_{\frac{1}{2}\anticommu{c^{\dagger}_{\alpha}}{c_{\gamma}} = \frac{1}{2}\delta_{\alpha\gamma}} - \frac{1}{2}c_{\gamma}c^{\dagger}_{\alpha} \tag{$\mathfrak{Tr}$1}. \label{eq:Trick1}
\]
\paragraph{The hopping term} This term can in the same way be expressed as:
\[
    \sum_{\langle ij\rangle\sigma} t_{ij} c_{i\sigma}^{\dagger} c_{j\sigma} = \frac{1}{2}\sum_{\langle ij\rangle \sigma} t_{ij} \left(c_{i\sigma}^{\dagger}c_{j\sigma} - c_{j\sigma}c_{i\sigma}^{\dagger}\right).
\]
This has to be done so that the $\gamma$ operators respect the fermionic anticommutation relations. The same method is involved for the chemical potential term.\\
We can also take the liberty to reorder the indices and use the fact that $t_{ij} = t_{ji}^{\ast}$:
\begin{equation}\label{eq:SymHam_tij}
    \sum_{\langle ij\rangle\sigma} t_{ij} c_{i\sigma}^{\dagger} c_{j\sigma} = \frac{1}{2}\sum_{\langle ij\rangle \sigma} t_{ij}c_{i\sigma}^{\dagger}c_{j\sigma} - t_{ij}c_{i\sigma}c_{j\sigma}^{\dagger} = \frac{1}{2}\sum_{\langle ij\rangle \sigma} t_{ij}c_{i\sigma}^{\dagger}c_{j\sigma} - t_{ij}^{\ast}c_{i\sigma}c_{j\sigma}^{\dagger}.
\end{equation}
\paragraph{The superconducting term} This term takes the following form:
\begin{equation}\label{eq:SymHam_Delta}
\sum_{i} \Delta_i c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger} + \Delta_i^{\ast} c_{i\uparrow}c_{i\downarrow}
        = \frac{1}{2}\sum_{i} \Delta_i \left(c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger}-c_{i\uparrow}^{\dagger}c_{i\downarrow}^{\dagger}\right)+ \Delta_i^{\ast} \left(c_{i\uparrow}c_{i\downarrow}-c_{i\downarrow}c_{i\uparrow}\right).
\end{equation}
We then finish this section by using Eq.\ref{eq:SymHam_muTerm}, \ref{eq:SymHam_tij} and \ref{eq:SymHam_Delta} in the Hamiltonian and obtain the following form:
\begin{equation}\label{eq:Ham_Symm_Supercond_1}
    \begin{aligned}
    H = E_0 ~-~& \frac{1}{2} \sum_{i\sigma} \mu_i\left(c_{i\sigma}^{\dagger}c_{i\sigma} - c_{i\sigma}c_{i\sigma}^{\dagger}\right)\\
    -& \frac{1}{2}\sum_{\langle ij\rangle \sigma} t_{ij}c_{i\sigma}^{\dagger}c_{j\sigma} - t_{ji}^{\ast}c_{i\sigma}c_{j\sigma}^{\dagger}\\
    -& \frac{1}{2}\sum_{i} \Delta_i \left(c_{i\downarrow}^{\dagger}c_{i\uparrow}^{\dagger}-c_{i\uparrow}^{\dagger}c_{i\downarrow}^{\dagger}\right) +
    \Delta_i^{\ast} \left(c_{i\uparrow}c_{i\downarrow}-c_{i\downarrow}c_{i\uparrow}\right).
    \end{aligned}
\end{equation}
The constant term $\frac{1}{2} \sum_{i\sigma} \mu_i$ of the normal Hamiltonian just vanished in the $E_0$.
We can now rewrite the Hamiltonian in a more compact way:
\begin{align}
    H = E_0 - \frac{1}{2}\sum_{i,j} \hat{c}_i^{\dagger} \hat{H}_{ij} \hat{c}_j  \label{eq:BdG_sys_H}
\end{align}
where the on site matrix reads
\begin{align}
    \hat{H}_{ij} = \begin{pmatrix}
        \mu_i \mathbb{I}_2 \delta_{ij} + t_{ij} & -\im\sigma_2\Delta_i \delta_{ij}\\
        \im\sigma_2\Delta^{\ast}_i \delta_{ij} & -\mu_i \mathbb{I}_2 \delta_{ij} - t_{ij}^{\ast}
    \end{pmatrix} = \begin{pmatrix}
        H_{ij} & \Delta_{ij}\\
        \Delta_{ij}^{\dagger} & -H_{ij}^{\ast}
    \end{pmatrix}    \label{eq:H^_ij} 
\end{align}
where we use $\mathbb{I}_n$ as an $n$-dimensional identity matrix. We haven't explicitly removed the 
$t_{ij}$ if we're not considering nearest neighbours.
At this point it's interesting to note that if we wish to build some periodic boundary conditions, 
it might be the case that a site on a side is neighbour with a site on the other side.\\  

We can further compress our $\hat{c}_i$ operator by introducing 
\[
    \check{c} = (\hat{c}_1,..,\hat{c}_N)
\] 
along with the system Hamiltonian-matrix $\check{H}_{ij}$ that orders the $\hat{H}_{ij}$ matrices together.  
Please note that $\check{H}_{ij}$ corresponds to an entry of $\hat{H}_{ij}$. The later maps two sites $i,j$ to a $4\times4$ matrix while the second concatenate all the matrices.\\
In $\check{H}_{ij}$ taking the entries $a=4(i-1) + 1$ to $4(i-1) + 4$ and $b=4(j-1) + 1$ to $4(j-1) + 4$ corresponds to $\hat{H}_{ab}$ if $a$ is the site $i$ and $b$ the site $j$.
This allows us to rewrite the Hamiltonian $\ref{eq:BdG_sys_H}$ as:
\begin{align}
    H = E_0 - \frac{1}{2} \check{c}^\dagger \check{H} \check{c}.
\end{align}
\subsection{Eigenvalues}
We now have a look at the following eigenvalue problem, which later helps from the diagonalization of the Hamiltonian:
\begin{equation}
    \label{eq:BdG_eigenVal_H} 
    \check{H} \check{\chi}_n = E_n \check{\chi}_n,
\end{equation}
$n$ runs over the number of the eigenvalue and $\check{\chi}_n$ is the corresponding eigenvector.
We can decompose the $\check{\chi}_n$ to reflect each lattice site: $\check{\chi}_n = (\hat{\chi}_{n1},..,\hat{\chi}_{nN})$. 
This means $\chi_{ni}$ refers to a $4\times4$ block, i.e. the on the sub-matrix we had earlier talked about.
Therefore, this $\chi_{ni}$ contains four values, grouped in two vectors of length two, one for each spin: $\chi_{n,i} = (u_{ni}, v_{ni})$.
Further $u_{ni} = (u_{ni\uparrow}, u_{ni\downarrow})$ couples to the two first components $(c_{i\uparrow},c_{i\downarrow})$ we had in $\hat{c}$ and 
similarly $v_{ni} = (v_{ni\uparrow}, v_{ni\downarrow})$ to the two last components $(c_{i\uparrow}^{\dagger},c_{i\downarrow}^{\dagger})$ of
the four operator $\hat{c}$. These values represent the coherence factors we defined in Eqs.\ref{eq:coherenceFac_v} and \ref{eq:coherenceFac_u}.\\ 

We can simplify the eigenvalue problem by only taking a look at a site $i$. We then sum up over $i$: 
\[
    \sum_{j\in\natset{N}}\hat{H}_{ij} \hat{\chi}_{nj} = E_n \hat{\chi}_{ni}.
\]
To generalize we can sum over the rows of $\check{H}_{ij}$ with the components of $\check{\chi}_n$.
We remember that $\check{H}_{ij}$ represent a complex scalar and $\hat{H}_{ij}$ is a $4\times4$ matrix with complex entries.
 So it follows by reintroducing Eq.\ref{eq:H^_ij} the following set of equations:
\begin{equation}
    \left\{
    \begin{aligned}
        &\sum_{j\in\natset{N}}H_{ij} u_{nj} + \Delta v_{nj} = &E_n u_{nj}\\
        &\sum_{j\in\natset{N}}\Delta^{\dagger} u_{nj} - H_{ij}^{\ast} v_{nj} =~& E_n v_{nj}.
    \end{aligned}
    \right.~~
    \stackrel{(1)}{\longrightarrow}~~
    \left\{
        \begin{aligned}
            &\sum_{j} H_{ij} u_{nj} + \Delta v_{nj} ~=& E_n u_{nj}\\
            &\sum_{j} H_{ij} v_{nj}^{\ast} + \Delta^{\dagger} u_{nj}^{\ast}= &-E_n v_{nj}^{\ast}.
        \end{aligned}
        \right.
\end{equation}
Where in (1) we took the conjugate of the second equation and used $\Delta^{\dagger} = -\Delta^{\ast}$.
This is an important result, because it shows that if $\check{\chi}_n = (u_{n1}, v_{n1},u_{n2}, v_{n2},.. )$ 
is an eigenvector with eigenvalue $E_n$, then  
so should be $(v_{n1}^{\ast}, u_{n1}^{\ast},v_{n2}^{\ast}, u_{n2}^{\ast},.. )$ with the eigenvalue $-E_n$.\\

This leads to a symmetry in the energy spectrum of $H = E_0 \pm \frac{1}{2}\check{c}^{\dagger}\check{H}\check{c}^{\dagger}$.
A flexibility which allows us to choose the version of $H$ with the positive sign, which is more commonly used.\\

\subsection{Diagonalization} \label{sec:Diagonalization}
Our goal is now to express the Hamiltonian relative to its energy eigenvalues, which is more particle to work with.
As we have seen in the last section, eigenvectors $\chi_n$ allows us to compute the energies.\\

First we define a matrix from all the eigenstates $\check{X} = [\check{\chi}_{\pm 1},..,\check{\chi}_{\pm 2N}]$.
We then introduce a matrix $\check{D} = \text{diag}(E_{\pm 1},..,E_{\pm 2N})$ with the eigenvalues sorted on the diagonal. The order in which the eigenvectors appear is not important
but $\check{\chi}_{i}$ should be on the same column index as $E_{i}$ not to lose track of which eigenvector is linked with which eigenvalue.
Then, assuming that the Hamiltonian can be diagonalized, we can write it as:
\begin{equation}\label{eq:Diag_Ham}
    \check{H} = \check{X}\check{D}\check{X}^{-1} = \check{X}\check{D}\check{X}^{\dagger} 
\end{equation}
where we used the fact that .\\
The eigenvalues correspond to the energies of the system, this means they should be real because they correspond to a physical quantity. The above expression
is equivalent to saying that $\check{H}$ is hermitian. Hermitian matrices are known to have real eigenvalues and can be represented with a unitary matrix $\check{X}$. \rem{cite?} 
We can then transform the Hamiltonian with $\check{c} := \check{X}\check{\gamma}$
\begin{align*}
    H = E_0 + \frac{1}{2}\check{c}^{\dagger}\check{H}\check{c} =& E_0 + \frac{1}{2}\check{\gamma}^{\dagger}\check{X}^{\dagger}\check{H}\check{X}\check{\gamma}\\
    =& E_0 +\frac{1}{2}\check{\gamma}^{\dagger}\underbrace{\check{X}^{\dagger} \check{X}}_{=\mathbb{I}}\check{D}\underbrace{\check{X}^{-1}\check{X}}_{=\mathbb{I}}\check{\gamma}\\
    =& E_0 + \frac{1}{2}\check{\gamma}^{\dagger}\check{D}\check{\gamma}\\
    =& E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}}E_n \gamma_n^{\dagger}\gamma_n\\
\end{align*}
where $\mathcal{N}= \{\pm n : n \in \natset{N}\}$
Rearranging the transformation of $\check{c}$, we get $\gamma = \check{X}^{\dagger}\check{c}$.   
Now that we've made the structure of the involved variables clear in the last section, we find the expression of the $\gamma$ which is $2N$-dimensional. A component of $\gamma$ is:
\begin{align*}
    \gamma_n &= \sum_{i} \left( u_{ni\uparrow}^{\ast}c_{i\uparrow}+ v_{ni\uparrow}^{\ast}c_{i\uparrow}^{\dagger} +  u_{ni\downarrow}^{\ast}c_{i\downarrow}+ v_{ni\downarrow}^{\ast}c_{i\downarrow}^{\dagger}\right)\\
        &=  \sum_{i\sigma} \left( u_{ni\sigma}^{\ast}c_{i\sigma}+ v_{ni\sigma}^{\ast}c_{i\sigma}^{\dagger}\right),
\end{align*}
and due to the symmetry we saw earlier, 
\[
    \gamma_{-n} =  \sum_{i\sigma} \left( v_{ni\sigma}c_{i\sigma}+ v_{ni\sigma}c_{i\sigma}^{\dagger}\right)
\]
for $n\in \natset{N}$. We now take a look at the conjugate transpose of $\gamma_{-n}$. Because scalar are dimension $1\times1$ we have 
$(uc^{\dagger})^{\dagger} = (c^{\dagger})^{\dagger} u^{\dagger} =  c u^{\ast} = u^{\ast}c$ and it follows:
\[
    \gamma_{-n}^{\dagger} = \sum_{i\sigma} \left( v_{ni\sigma}^{\ast}c_{i\sigma}^{\dagger}+ u_{ni\sigma}^{\ast}c_{i\sigma}\right) = \gamma_n.
\]
Using this we can link each $\gamma_i$ to the corresponding eigenvalue $E_i$:  $\gamma_n$ to the corresponding eigenvalue $E_n$ and $\gamma_{n-}$ 
to the corresponding eigenvalue $E_{-n} = -E_n$.
We recall that we had $2N$ degrees of freedom $c_{i\sigma}$ due
to the two possible spins, but after the transformation we get $4N$ degrees into $\hat{c}_i$ nevertheless. 
But because our energies $E_n$ and $E_{-n}$ are related to each other, we can keep only the positive $2N$ eigenvalues
and this maintain the total number of degree of freedom.\\

We can now apply this statement into the expression. First we can split the sum over the $n\in\mathcal{N}$ in two parts: $\mathcal{N}_+ = \{n \in \mathcal{N} : n> 0 \}$ and
 $\mathcal{N}_- = \{n \in \mathcal{N} : n<0 \}$.
\begin{align*}
    H &= E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma^{\dagger}_n\gamma_n + \frac{1}{2}\sum_{n\in\mathcal{N}_-} E_n \gamma^{\dagger}_n\gamma_n\\
      &= E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma^{\dagger}_n\gamma_n + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_{-n} \gamma^{\dagger}_{-n}\gamma_{-n}\\
      &= E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma^{\dagger}_n\gamma_n - \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma^{\dagger}_{-n}\gamma_{-n}\\
      &= E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma^{\dagger}_n\gamma_n - \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \gamma_{n}\gamma^{\dagger}_{n}\\
      &= E_0 + \frac{1}{2}\sum_{n\in\mathcal{N}_+} E_n \left( \gamma^{\dagger}_n\gamma_n -\gamma_{n}\gamma^{\dagger}_{n}\right).
\end{align*}
We used the energy symmetry $E_{-n} = -E_n$, $\gamma^{\dagger}_{-n} =\gamma_{n}$, as well as $\gamma_{-n} =\gamma^{\dagger}_{n}$.\\

Using this knowledge, we can express a final formula for the Hamiltonian by using the anticommutation properties of the fermionic $\gamma$-operators:
 $\anticommu{\gamma^{\dagger}_n}{\gamma_{n}} = 1$, so using the trick \ref{eq:Trick1} and bringing the $\frac{1}{2}$ prefactor in the sum:
\begin{align}
    H =& E_0 - \sum_{n\in \natset{N}} E_n \left( \gamma_n^{\dagger}\gamma_n - \frac{1}{2}\right).
\end{align}
This is the final form of the Hamiltonian in the Bogoliubov-de Gennes formalism. As a user one should build the Hamiltonian 
and computes its eigenvalues,-vector and use them to compute some physical quantities.\\
\subsection{Physical Quantities}
\subsubsection{Superconducting Gap}
We already covered how the superconducting gap $\Delta$ is a relevant property of the Meissner state. We now aim to use the  mean field 
theory in order to find the gap. This requires a self-consistency equation, which we can be derived from the Hamiltonian.\\ 

The gap was defined as $\Delta(\bm{r}) := U(\bm{r}) \langle \psi_{\uparrow}(\bm{r})\psi_{\downarrow}(\bm{r})\rangle$. Back to the tight binding formalism,
the gap now depends on the lattice site $i$ and reads
$\Delta_i = U_i\langle c_{i\uparrow}c_{i\downarrow}\rangle$, and we can express $c_{i\sigma}$ in terms of the $\gamma$-operators:\\
\begin{center}
\begin{minipage}{0.4\textwidth}
\begin{equation}
    \begin{aligned}\label{eq:BdG_transf_c}
    c_{i\sigma} =& \sum_{n\in\mathcal{N}} u_{ni\sigma}\gamma_n \\
        =& \sum_{n\in\mathcal{N}_+} u_{ni\sigma}\gamma_n + u_{-n,i\sigma}\gamma_{-n}\\
        =& \sum_{n\in\mathcal{N}_+} u_{ni\sigma}\gamma_n + v_{ni\sigma}^{\ast}\gamma_{n}^{\dagger}
    \end{aligned}
\end{equation}
\end{minipage}\hspace{0.05\textwidth}
\begin{minipage}{0.03\textwidth}
    \begin{tikzpicture}
        \coordinate (a) at (0,1);
        \coordinate (b) at (0,-1);
        \draw[-] (b) -- (a);
        \filldraw[color=black, fill = white , thin] (a) circle (0.05);
        \filldraw[color=black, fill = white , thin] (b) circle (0.05);
    \end{tikzpicture}
\end{minipage}
\begin{minipage}{0.45\textwidth}
    \begin{equation}
        \begin{aligned}\label{eq:BdG_transf_c_dagg}
        c_{i\sigma}^{\dagger} =& \sum_{n\in\mathcal{N}_+}( u_{ni\sigma}\gamma_n)^{\dagger} +( v_{ni\sigma}^{\ast}\gamma_{n}^{\dagger})^{\dagger} \\
            =& \sum_{n\in\mathcal{N}_+} \gamma_n^{\dagger}u_{ni\sigma}^{\dagger} + \gamma_{n}(v_{ni\sigma}^{\ast})^{\dagger} \\
            =& \sum_{n\in\mathcal{N}_+} u_{ni\sigma}^{\ast}\gamma_n^{\dagger} + v_{ni\sigma}\gamma_{n} \\
        \end{aligned}
    \end{equation}
\end{minipage}
\end{center}

where we used the symmetry of the eigenvectors. We can now compute expectation value involved in the gap by taking the termal average and the quantum expectation value:
\begin{equation}\label{eq:transfo_c_up_c_down_BdG}
\begin{aligned}
    \langle c_{i\uparrow}c_{i\downarrow} \rangle =& \sum_{n,m\in\mathcal{N}_+} \left\langle\left(u_{ni\uparrow}\gamma_n + v_{ni\uparrow}^{\ast}\gamma_{n}^{\dagger}\right)\left(u_{mi\downarrow}\gamma_m + v_{mi\downarrow}^{\ast}\gamma_{m}^{\dagger}\right)\right\rangle\\
     =&  \sum_{n,m\in\mathcal{N}_+} \left\langle\left(u_{ni\uparrow} u_{mi\downarrow}\gamma_n\gamma_m + u_{ni\uparrow} v_{mi\downarrow}^{\ast}\gamma_n\gamma_{m}^{\dagger} + v_{ni\uparrow}^{\ast}u_{mi\downarrow}\gamma_{n}^{\dagger} \gamma_m+  v_{ni\uparrow}^{\ast} v_{mi\downarrow}^{\ast}\gamma_{n}^{\dagger}\gamma_{m}^{\dagger}  \right)\right\rangle\\
     \stackrel{(\ast)}{=}&  \sum_{n\in\mathcal{N}_+} \left\langle u_{ni\uparrow} v_{ni\downarrow}^{\ast}\gamma_n\gamma_{n}^{\dagger}\right\rangle + \left\langle v_{ni\uparrow}^{\ast}u_{ni\downarrow}\gamma_{n}^{\dagger}\gamma_{n}\right\rangle\\     
     =&  \sum_{n\in\mathcal{N}_+} u_{ni\uparrow} v_{ni\downarrow}^{\ast}\left\langle\gamma_n\gamma_{n}^{\dagger}\right\rangle + v_{ni\uparrow}^{\ast}u_{ni\downarrow}\left\langle \gamma_{n}^{\dagger}\gamma_{n}\right\rangle\\
     =&  \sum_{n\in\mathcal{N}_+} u_{ni\uparrow} v_{ni\downarrow}^{\ast} \left(1-f(E_n)\right) + v_{ni\uparrow}^{\ast}u_{ni\downarrow}f(E_n)
\end{aligned}
\end{equation}
where $f$ is the Fermi-Dirac distribution. In $(\ast)$ we notice no $\gamma\gamma$ or $\gamma^{\dagger}\gamma^{\dagger}$ terms in the Hamiltonian, so their expectation 
value is zero\footnote{This is like the expectation value of killing twice a fermion in a state. It is not possibilities, because we can't annihilate a state that has a possession number of zero.
And in the same way due to the Pauli principle we can't have more than one particle in the same state, so $\langle \gamma^{\dagger} \gamma^{\dagger} \rangle = 0$. We are not 
finding these terms in the Hamiltonian. Here we removed the indices, in fact the diagonally also takes place on the indices so that we end just with $n$.
The Hamiltonian is diagonal in the quasiparticles' operators.}.\\
\rem{If we diagonalize a positive matrix and use positive eigenvalues, there is no trace of the attraction. Moreover, the gap keeps switching sign on every iteration.
Then can be solved by using a negative $U$. But then we have a mismatch between the gap and the hopping, chemical potential, etc definition. The solution was to diagonalize
negative matrices or propagate the minus sign to the energies eigenvalues. (but still take the eigenvectors associated with the positive eigenvalues).}\\

The expectation value $\langle a\hat{A}\rangle_{\Phi}$ of a scalar times an operator reads $\langle \Phi|a \hat{A}|\Phi\rangle_{\Phi} = a \langle \Phi|\hat{A}|\Phi\rangle_{\Phi} = a \langle \hat{A}\rangle_{\Phi}$. 
To convince ourselves, we just take a look at the first quantization expression of this braket. This result leads to the self-consistency equation:
\begin{equation}\label{eq:SelfConsitentDelta}
    \Delta_i = U_i\sum_{n\in\mathcal{N}_+} u_{ni\uparrow} v_{ni\downarrow}^{\ast} \left(1-f(E_n)\right) + u_{ni\downarrow} v_{ni\uparrow}^{\ast}f(E_n)
\end{equation}
We plan to solve this equation numerically, inserting some guess in the Hamiltonian, diagonalize it, update $\Delta_i$ and reinsert it into H. We should repeat this 
until we reach a fix point or the desired accuracy.\\
\end{document}

