\documentclass[../main.tex]{subfile}
\begin{document}
\section{An unconventional superconductivity}\label{sec:appendix}
\subsection{Site dependent potential}
In this section we are going to highlight how the neighbour-depending potential can lead to a new kind of superconductivity. Among others, we are going to discuss the $d$-
wave superconductivity which shares similarities with more exotic magnets, such as the altermagnet. 
Indeed, the spatial repartition of the phase of the gap shares a similar geometry with the spin polarization of the altermagnet.
\begin{figure}[H]
    \centering
    \begin{tikzpicture}
        \coordinate (A) at (5,0);
        \coordinate (B) at (0,0);
        \coordinate (o) at (0,-3);   
        \draw[draw=red, very thick] ($(A)+(1,0)$) arc[x radius = 1, y radius = 2 , start angle=180, end angle=-180] ;
        \draw[draw=blue, very thick] (A) arc[x radius = 2, y radius = 1, start angle=180, end angle=-180,] ;
        \node[anchor = center, color = red] at ($(A)+(2,1.5)$) {$\bm{\uparrow}$};
        \node[anchor = center, color = blue] at   ($(A)+(3.5, 0)$) {$\bm{\downarrow}$};
        \node[anchor = center, color = black] at   ($(A)+(2.5, -2.2)$) {AM momenta repartition};

        \draw[draw=red, very thick] ($(B)+(1,0)$) arc[x radius = 1, y radius = 2 , start angle=180, end angle=-180] ;
        \draw[draw=blue, very thick] (B) arc[x radius = 2, y radius = 1, start angle=180, end angle=-180,] ;
        \node[anchor = center, color = red] at ($(B)+(2,1.5)$) {$\bm{+}$};
        \node[anchor = center, color = blue] at   ($(B)+(3.5, 0)$) {$\bm{-}$};
        \node[anchor = center, color = black] at   ($(B)+(2.5, -2.2)$) {$d$-wave in momentum space};

        \draw[->, thick] (o) -- ($(o)+(1,0)$) node[anchor = north]{$k_x$};
        \draw[->, thick] (o) -- ($(o)+(0,1)$) node[anchor = east]{$k_y$};
    \end{tikzpicture}
    \caption{The positive and negative phase of the unconventional $d$-wave superconductive gap, as well as the spin splitting of the altermagnet in momentum space.
    The intersection of the lines are called nodes. A line from the centre to the node is called a nodal line. 
    In a proximity system if the Cooper pairs enters the non-superconducting material 
    along the nodal lines, we expect no preferred phase, as it could be if we enter from the left for example. Figure inspired by \cite{Smejkal2022}.}
\end{figure}

The derivations we are going to make are closely based on the work of A. H. Mjøs and J. Linder in \cite{Mjos2019}.

The Hamiltonian being the ground stone of this 
discussion, we're going to begin with it. It differs slightly from the symmetric one we derived in Eq. \ref{eq:Ham_Symm_Supercond_1}. This extended version contains a neighbour-depending potential 
$H_V$ that is going to 
produce the new superconductive $\Delta$-part of the Hamiltonian. This potential is as well attractive such that $V>0$, similar to the BCS theory.
\begin{equation}
    H = -t\sum_{\langle ij\rangle \sigma} c_{i\sigma}^{\dagger}c_{j\sigma} - \mu \sum_{i\sigma} c_{i\sigma}^{\dagger}c_{i\sigma} - \frac{V}{2} \sum_{\langle ij\rangle \sigma} n_{i\sigma}n_{j\bar{\sigma}}.
\end{equation}
Here the $\bar{\sigma}$-notation means the opposite spin of $\sigma$. In other words the attraction finds only place between particles of opposite spin,
 mirroring the formation process of Cooper-pairs.
We have a factor of one half to avoid counting twice the neighbours.\\

Trained eyes will recognize that $H_V$ is not quadratic in the creation and annihilation operators which makes the Hamiltonian impossible to write in the BdG-formalism. For this reason we can 
use the so called Hartree-Fock mean field approximation $H_V \rightarrow H^{HF}_V$ defined as:
\begin{equation}
    H^{HF}_V = -\frac{1}{2} \sum_{\langle ij\rangle \sigma} V_{ij} \left(F_{ij}^{\sigma \bar{\sigma}} c^{\dagger}_{j\bar{\sigma}}c^{\dagger}_{i\sigma} + \text{h.c.} 
    + |F_{ij}^{\sigma \bar{\sigma}}|^2\right),
\end{equation}
involving the pairing amplitude $F_{ij}^{\sigma \bar{\sigma}} = \langle c_{i\sigma}c_{j\bar{\sigma}}\rangle$ that we already introduced. The $V_{ij}$ are the neighbour-depending potential.
The last term is a constant energy term, which we can discard during the diagonalization process. If one wanted to compute the free energy this must be included there.
From this point simplifications can be made to reach out final Hamiltonian.\\

Using the fermionic property $[c_{i\sigma}^{\dagger},c_{j\sigma}^{\dagger}]_+ = 0$ we have $c_{i\sigma}^{\dagger} c_{j\sigma}^{\dagger} = -c_{i\sigma}^{\dagger} c_{j\sigma}^{\dagger}$
which leads to $\langle  c_{i\sigma}^{\dagger} c_{j\sigma}^{\dagger} \rangle = -\langle c_{i\sigma}^{\dagger} c_{j\sigma}^{\dagger}\rangle$. We can use this in the last step of the following simplification:
\begin{equation}\label{eq:HF_V}
    \begin{aligned}
        H^{HF}_V =& -\frac{1}{2} \sum_{\langle ij\rangle \sigma} V_{ij} \left(F_{ij}^{\sigma \bar{\sigma}} c^{\dagger}_{j\bar{\sigma}}c^{\dagger}_{i\sigma} + \text{h.c.}\right)\\
            =& -\frac{1}{2}\sum_{\langle ij\rangle} V_{ij} \left(F_{ij}^{\uparrow \downarrow} c^{\dagger}_{j\downarrow}c^{\dagger}_{i\uparrow} + F_{ij}^{\downarrow\uparrow} c^{\dagger}_{j\uparrow}c^{\dagger}_{i\downarrow} + \text{h.c.}\right)\\
            =& -\sum_{\langle ij\rangle} V_{ij} \left(F_{ij}^{\uparrow \downarrow} c^{\dagger}_{j\downarrow}c^{\dagger}_{i\uparrow} + \text{h.c.}\right)
    \end{aligned}
\end{equation}
Using the relation $F_{ij}^{\uparrow\downarrow} = -F_{ij}^{\downarrow\uparrow}$ and the symmetry of the potential $V_{ij} = V_{ji}$ we can add the two terms up and remove the one half factor.
We fix the spins in the pairing amplitude and define $F_{ij} = F_{ij}^{\uparrow\downarrow}$.
The Hamiltonian is now ready to be diagonalized but first, we are going to discuss which advantages a Fourier transform of the Hamiltonian could bring us.\\
 
In a homogenous material we can consider a lattice and imagine some periodic boundary conditions in all directions. There is a translation invariance.
In heterostructures however the material may vary, let's assume
without loss of generality, in a direction. As we now, a periodic signal is a good candidate for a Fourier transform, which we can then express in a finite set of coefficient. 
This is very practical.
However, the direction we want to transform on has to show a periodicity. For this reason homogenous two-dimensional lattice involves a Fourier transformation in two space dimensions while a heterostructure
we transform only in the direction where the material is the same. For instance a multilayer material in the $x$-direction can be described by combining a real space description in the $x$-axis 
combined to a Fourier transformation in the $y$-direction.
In this thesis we are going to focus ourselves on a multilayer material in the $x$-direction.\\

\subsection{In the vertical periodic boundary setup}\label{sec:Vertical_Fourier}
We assume we have a lattice of $N_x\times N_y$ sites.
The description of the creation and annihilation operators with a step in the momentum space for the $y$-direction can be expressed as follows:
\begin{align}
    c_{xy\sigma} =& \frac{1}{\sqrt{N_y}} \sum_{k_y} c_{x k_y\sigma} e^{\im k_y y} \label{eq:C_Foruier}\\
    c^{\dagger}_{xy\sigma} =& \frac{1}{\sqrt{N_y}} \sum_{k_y} c^{\dagger}_{x k_y\sigma} e^{-\im k_y y}\label{eq:C_dagg_Foruier}
\end{align}
How do we find an expression for $k_y$? The periodicity (for example in the $c$ operator) yields 
$c_{xy\sigma} = c_{x,y+N_x,\sigma}$ this means the following condition must be fulfilled:
\begin{align*}
    c_{xy\sigma} = c_{x,y+N_x,\sigma} \Leftrightarrow &e^{\im k_y y} = e^{\im k_y (y+N_y)} \Leftrightarrow e^{\im k_y N_y} = 1\\
    \Leftrightarrow &k_y = \frac{2\pi n}{N_y}.
\end{align*}

We know that the momentum index should cover the entire first Brillouin zone. This covers the momentum from $-\pi/a$ to $\pi/a$ 
where $a$ is the lattice constant. Further due to the $2\pi/a$ periodicity we have the same $k_y$ at $-\pi/a$ and $\pi/a$.
For this reason we need to map $k_y $ in $[-\pi/a ;\pi/a)$.
This means we have $n\in \left[-N_y/2  ; N_y/2-1\right]$ including $0$. For $n=4$ we then have $k_y\in\{ -\pi, -\pi/2, 0,  \pi/2\}$. \\

For the readability we are going to use $k_y \rightarrow k$.
Further to an index $i$  can associate $(x,y)$ and to $j$, $(x',y')$.
We first want to transform the hopping term:
\begin{equation*}
    H_{\text{hop}} = -\sum_{\langle ij\rangle \sigma} t_{ij} \sum_{kk'} c^{\dagger}_{x k\sigma} c_{x' k'\sigma} e^{\im (k' y' - k y)}
\end{equation*}
Here we can use the neighbour shift properties $y' = y + \delta_y$ where $\delta_y = \pm 1$. Doing so we have 
\[
    e^{\im (k' y' - k y)} = e^{\im (k' (y+\delta_y) -  k y)} = e^{\im (k' -  k)y}e^{\im k'\delta_y}
\]
No wee need to express the neighbourhood sum. Precisely we have
\begin{align*}
        H_{\text{hop}} =& -\sum_{\langle ij\rangle \sigma} t_{ij} \sum_{kk'} c^{\dagger}_{x k\sigma} c_{x' k'\sigma}  e^{\im (k -  k')y}e^{\im k'\delta_y}\\
                        =& -\sum_{xy \sigma} \sum_{kk'}  \biggl( t_{x,x+1} \underbrace{c_{x k\sigma}^{\dagger} c_{x+1 k'\sigma}e^{\im k'\cdot (0)}}_{\text{$+x$ hopping, no $\delta_y$}} +  t_{x,x-1} \underbrace{c_{x k\sigma}^{\dagger} c_{x-1 k'\sigma} e^{\im k'\cdot (0)}}_{\text{$-x$ hopping, no $\delta_y$}}\\
                        & ~~~~~~~~~~~~+t_{x,y-1} \underbrace{c_{x k\sigma} c_{x k'\sigma}^{\dagger} e^{\im k'\cdot (-1)}}_{\delta_y = -1} + t_{x,y+1} \underbrace{c_{x k\sigma}^{\dagger} c_{x k'\sigma}e^{\im k'\cdot (1)}}_{\delta_y = 1}\biggr)e^{\im (k -  k')y}
\end{align*}
As we see the $y$ direction is now expressed in the $k$-index, which is unique for each lattice $y$-slice. The information is then conserved. 
We know that system has different material on the $x$ axis. This means $t_{x,y-1} = t_{x,x} = t_{x,y+1}$ because the material are isotropic in $y$. Every material has a 
different hopping term nevertheless. Besides, we can use the following relation $1/N_y \sum_{y} e^{\im (k -  k')y} = \delta_{kk'}$. Performing both expression leads after a summation over $k'$ to
\begin{equation*}
    H_{\text{hop}} = -\sum_{x k \sigma} t_{x,x+1} c_{x k\sigma}^{\dagger} c_{x+1 k\sigma} + t_{x,x-1} c_{x k\sigma}^{\dagger} c_{x+1 k\sigma} +  t_{x,x} c_{x k\sigma}^{\dagger} c_{xk\sigma}\left(e^{\im k} + e^{-\im k}\right)
\end{equation*}
And now we can reintroduce an arbitrary second coordinate $x'$ to describe the neighbours.
\begin{equation}
    H_{\text{hop}} = -\sum_{xx' k \sigma} t_{x,x'} c_{x k\sigma}^{\dagger} c_{x' k\sigma} \left(\delta_{x+1,x'} + \delta_{x-1,x'} + \delta_{x,x'} 2 \cos(k)\right)
\end{equation}
The chemical potential term is more easily given. In fact the number operator yields to use two operators $c^{\dagger}c$ at a same coordinate $i$.
\begin{equation}
    H_{\mu} = -\mu \sum_{x kk' \sigma} c_{x k\sigma}^{\dagger} c_{x k'\sigma} e^{\im (k-k')y} = -   \sum_{xx'k\sigma} \mu c_{xk\sigma}^{\dagger} c_{xk'\sigma} \delta_{xx'}     
\end{equation}
We finally have for the terms involving $c^{\dagger}_{xx'\sigma} c_{xx'\sigma}$:
\begin{equation*}
    H_{\text{hop}} + H_{\mu} = \sum_{xx'k\sigma} \epsilon_{xx'k\sigma} c_{xk\sigma}^{\dagger} c_{x'k\sigma}
\end{equation*}
using
\[
    \epsilon_{xx'k\sigma}= - t_{xx'} \left(\delta_{x+1, x'} + \delta_{x-1,x'}\right) - \left(t_{xx'}2\cos(k) + \mu\right) \delta_{xx'}
\]

Moving on to the potential term we have to introduce a new notation. The goal is to describe a displacement in a direction from a point. So assuming
we follow the indexing introduced in Fig. \ref{fig:Sim_System}: $i\pm\hat{x} = i\pm 1$ and $i\pm\hat{y} = i\pm N_x$.
For the brevity we use $f(a) = V_{ia}F_{ia} c^{\dagger}_{a\downarrow} c^{\dagger}_{i\uparrow}$. Still assuming that $V_{ij}>0$ and that the interaction is attractive, we have:
\begin{align*}
    H_V =& -\sum_{\langle ij\rangle} V_{ij} F_{ij} c^{\dagger}_{i\downarrow} c^{\dagger}_{j\uparrow} + \text{h.c.} \\
    =& -\sum_{i} f(i-1) + f(i+1) + f(i+N_x) + f(i-N_x) + \text{h.c.}
\end{align*}
We can now insert our Fourier transformation introduced in Eq. \ref{eq:C_dagg_Foruier} and Eq. \ref{eq:C_Foruier} to obtain
\begin{align*}
    H_V =& -\sum_{xy} \frac{1}{N_y} \sum_{kk'} \left( V_{x,x+1} F_{x}^{x+} c^{\dagger}_{x+1,k,\downarrow}c^{\dagger}_{xk'\uparrow} + V_{x,x-1} F_{x}^{x-} c^{\dagger}_{x+1,k,\downarrow} c^{\dagger}_{xk'\uparrow} \right.\\
        &+ \left.V_{xx}\left( F_{x}^{y+} e^{-\im k}  - F_{x}^{y-} e^{\im k}\right) c^{\dagger}_{xk\downarrow} c^{\dagger}_{xk'\uparrow} \right) e^{-\im(k + k')y} + \text{h.c.}\\
\end{align*}
Defining a more general form for the summand involving two sites $i$ and $j$:
\begin{equation*}
    \begin{aligned}
    F_{xx'k} =&  V_{x,x'}\left( F_{x}^{x+} \delta_{x+1,x'} +  F_{x}^{x-} \delta_{x-1,x'}\right. \\
        &+ \left.\left( F_{x}^{y+} e^{-\im k}  - F_{x}^{y-} e^{\im k}\right)\delta_{xx'}\right),
    \end{aligned}
\end{equation*} 
where we got $k' = -k$ from the sum over the $y$-direction. We can rewrite the expression of $H_V$ as
\begin{align*}
    H_V =& -\sum_{x} \sum_{kk'} F_{xx'k} c^{\dagger}_{xk\uparrow} c^{\dagger}_{x',-k,\downarrow} + F_{xx'k}^{\ast} c_{x',-k,\downarrow} c_{xk\uparrow}.
\end{align*}
Now using $H_{\text{hop}}, H_{\mu}$ and $H_{V}$ we can write the full Hamiltonian as:
\begin{equation}
    \begin{aligned}
    H =& \sum_{xx'k} \hat{c}_{xk}^{\dagger} H_{xx'k} \hat{c}_{x'k}\\
      =& \sum_{xx'k} \begin{pmatrix}
        c^{\dagger}_{xk\uparrow} & c_{x,-k,\downarrow}
      \end{pmatrix}
        \begin{pmatrix}
            \epsilon_{xx'k\uparrow} & F_{xx'k}\\
            F_{xx'k}^{\ast} & -\epsilon_{xx'k\downarrow}
        \end{pmatrix}
        \begin{pmatrix}
            c_{x'k\uparrow}\\
            c^{\dagger}_{x',-k,\downarrow}
        \end{pmatrix}.
    \end{aligned}
\end{equation}
This is a base we can start to work with. However, the altermagnetic matrix has a more complex spin structure and can be described with these $\hat{c}$.
This requires additional work if we want to express the AM in a vertical periodic boundary setup.

The summation over all $x,x'$ can be represented in a new matrix.
\[
    H = \sum_k \check{c}_k^{\dagger} H_k \check{c}_k
\]
involving the $4Nx \times 4Nx$ matrix $H_k$ and the $4Nx$-dimensional vector $\check{c}_k$. 
\[
    H_k = \begin{pmatrix}
        H_{11k} &\dots & H_{1N_xk}\\
        \vdots&\ddots&\\
        H_{N_x1k} & & H_{N_xN_xk}
    \end{pmatrix}
\]
Please note that \cite{Mjos2019} uses the notation $D_k$ for $\check{c}_k$, but we don't want to confuse the reader with the already defined eigenvalues
 diagonal matrix of Eq. \ref{eq:Diag_Ham}.
As before the $y$ information is stored in the $k$-index, which is unique for each lattice $y$-slice. This said, we 
can diagonalize $N_y$ times a $4N_x \times 4N_x$ matrix. Each $H_k$ represents the interaction of a $y$-line with itself.
The eigenvalues are the same for each $y$-slices and the physical
quantities are going to be expressed with this summation over $k$ and the eigenvalues, -vectors of each $k$ ($y$-slice).\\

On the other hand the vector we use to carry the creation and annihilation operators is given as 
\[
    \check{c}_k^{\dagger} = \begin{pmatrix}
        c^{\dagger}_{1k\uparrow} & c_{1,-k,\downarrow}& \dots &c^{\dagger}_{N_x k\uparrow} & c_{N_x,-k,\downarrow}
    \end{pmatrix}\in\mathbb{H}^{2N_x}
\]

\subsubsection{BdG-transformation for a vertical Foruier transform}
The eigenvalues' equation is similar to Eq. \ref{eq:BdG_eigenVal_H}
\begin{equation}\label{eq:BdG_eigenVal_H_k}
    H_k \mathfrak{X}_{nk} = E_{nk} \mathfrak{X}_{nk}.
\end{equation}
The eigenvectors and -values are given as
\begin{equation*}
    \mathfrak{X}_{nk} = \begin{pmatrix}
        \mathfrak{x}_{n1k}\\
        \vdots\\
        \mathfrak{x}_{nN_xk}\\
    \end{pmatrix},~~ \mathfrak{x}_{nxk} = \begin{pmatrix}
        u_{nxk}\\
        v_{nxk}
    \end{pmatrix}.
\end{equation*}
If we stick to the formalism we already derived in the earlier Sec. \ref{sec:Diagonalization} we obtain similar 
eigenvectors where $u_{nxk}$ corresponds to $c_{xk\uparrow}$ and $v_{nik}$  $c_{x,-k,\downarrow}$ (see Eq. \ref{eq:eigenvectors_BdG_Fourier}). We are now going to transform the $c$ operators. First we need
to define $\mathfrak{X}_k = [\mathfrak{X}_{1k}, ..,\mathfrak{X}_{2N_xk}]\in\mathbb{H}^{2N_x\times 2N_x}$ storing the number of 
lattice sites times the number of spins (2) in the first dimension, and 
the number of eigenvectors in the second dimension. Besides, we have $\mathfrak{g}_k = (\mathfrak{g}_{1k}, .., \mathfrak{g}_{2N_xk})^T\in\mathbb{H}^{2N_x}$ along with $D_{k} = \mathfrak{X}_k\mathfrak{g}_k$,
delivering $\mathfrak{g}_k = \mathfrak{X}^{\dagger}_k D_{k}$ which is equivalent to:
\begin{equation}\label{eq:eigenvectors_BdG_Fourier}
    \mathfrak{g}_{nk} = \sum_{x\in{N_x}} u_{nxk}c_{xk\uparrow} + v_{nxk}c^{\dagger}_{x,-k,\downarrow}.
\end{equation}
Looking at $D_{k} = \mathfrak{X}_k\mathfrak{g}_k$ we can derive two very useful expressions:
\begin{center}
    \begin{minipage}{0.4\textwidth}
    \begin{equation}\label{eq:BdG_transf_c_fourier}
        c_{xk\uparrow} = \sum_{n\in\natset{2N_x}} u_{nxk}\mathfrak{g}_{nk} 
    \end{equation}
    \end{minipage}\hspace{0.05\textwidth}
    \begin{minipage}{0.03\textwidth}
        \begin{tikzpicture}
            \coordinate (a) at (0,0.5);
            \coordinate (b) at (0,-0.5);
            \draw[-] (b) -- (a);
            \filldraw[color=black, fill = white , thin] (a) circle (0.05);
            \filldraw[color=black, fill = white , thin] (b) circle (0.05);
        \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \begin{equation}
        \label{eq:BdG_transf_c_fourier_dagg}
            c_{x,-k,\downarrow}^{\dagger} =\sum_{n\in\natset{2N_x}} v_{nxk}\mathfrak{g}_{nk}. 
        \end{equation}
    \end{minipage}
    \end{center}
These are the equivalent of Eqs. \ref{eq:BdG_transf_c} and \ref{eq:BdG_transf_c_dagg} for the Fourier transformed $c$-operators along the $y$-axis.\\
\subsubsection{Pairing amplitudes}
For the derivation of the pairing amplitudes along the $x$ and $y$ axis shares similarities. Therefore, we embed the axis into the variable $a\in\{\hat{x},\hat{y}\}$.
With $F_i^{\pm a}$ we mean $F_i^{\pm \hat{x}}$ or $F_i^{\pm \hat{y}}$ which are equivalent to $F_{i,i\pm x}$ and $F_{i,i\pm y}$.
Doing so, we will use our BdG-transformation as we did earlier to be 
able to solve these parameters self-consistently using the eigenvectors and -values. We remember that the site $i$ has the coordinate $(x,y)$ and its neighbour $j$
the coordinate $(x',y')$.
\begin{align*}
    F_i^{\pm a} = \langle c_{i\uparrow} c_{i\pm a,\downarrow}\rangle =& \frac{1}{N_y} \sum_{kk'} \langle c_{x k\uparrow} c_{x\pm \delta_x,k',\downarrow} \rangle e^{\im(ky + k'y')}\\
                                                                    &   \frac{1}{N_y} \sum_{kk'} \langle c_{x k\uparrow} c_{x\pm \delta_x,k',\downarrow} \rangle e^{\im(k + k')y} e^{\pm\im k' \delta_y}
\end{align*}
using $y\pm \delta_y = y'$ and $x\pm \delta_x = x'$. Naturally we know that for $a = \hat{x}$ there is no hopping along the $y$-axis, such that $\delta_y=0$ and in the same way for $a = \hat{y}$ we have $\delta_x = 0$.
The expectation value is independent of the site vertical coordinate $y$. This means that we can achieve a site description 
by making the average of the value over a $x$-slice. In other words
we can write:
\begin{equation*}
    F^{\pm a}_i = 
    \frac{1}{N_y}\sum_{y\in\natset{N_y}} \frac{1}{N_y} \sum_{kk'} \langle c_{x k\uparrow} c_{x \pm \delta_x,k',\downarrow} \rangle e^{\im(k + k')\bm{r}_i} e^{\pm\im k'\delta_y}
\end{equation*}
which after the summation over $i$ yields, as we covered earlier, to $1/N_y \sum_{y} e^{\im(k + k')y} = \delta_{k,-k'}$:
\begin{equation*}
    F^{\pm x}_i = 
    \frac{1}{N_y} \sum_{k} \langle c_{x k\uparrow} c_{x\pm \delta_x,k,\downarrow} \rangle e^{\mp\im k\delta_y}.
\end{equation*}
Now that we have simplified the Fourier transform we can incorporate the BdG-transformation. The process is very similar to Eq. \ref{eq:transfo_c_up_c_down_BdG} and after doing this,
we obtain the following expression:
\begin{equation}\label{eq:transfo_F_x}
    F^{\pm a}_i =\frac{1}{N_y}\sum_{k}\sum_{nn'} u_{nx k}v_{n',x \pm \delta_x,k}^{\ast} \langle \mathfrak{g}_{nk} \mathfrak{g}_{n'k}^{\dagger} \rangle e^{\mp\im k \delta_y}
\end{equation}
Recalling the $a$ abstraction of the axis, we get:
\begin{align}
    F^{\pm x}_i =& \frac{1}{N_y} \sum_{nk} u_{nx k} v_{n,x\pm \delta_x,k}^{\ast}\left(1 - f(E_{nk})\right)\\
    F^{\pm y}_i =& \frac{1}{N_y} \sum_{nk} u_{nx k} v_{n x k}^{\ast}\left(1 - f(E_{nk})\right) e^{\mp \im k},
\end{align}
where $x\pm \delta_x$ means $x\pm1$.


\subsubsection{In the open boundary setup}
Here we need to reuse the equations of the Nambu-Spin formalism described in chapter \ref{sec:BdGFormalism}. As we saw we need to first
take care that the part of the Hamiltonian we want to introduce has to be hermitian. Moreover the eigenvectors need to respect the fermionic
anticommutation properties.
If we transform the Hartree-Fock Hamiltonian as it is in Eq. \ref{eq:HF_V} we see that only the upper right quadrant of the matrix $H_{V,ij}^{HF}$ 
of $\check{c}_i^{\dagger} \cdot (H_{V}^{HF})_{ij}\cdot \check{c}_j $ is filled. We need to use the anticommutation relations to solve this.
This delivers the following expression:
\begin{equation}
    \begin{aligned}
    H_V^{HF} =& -\sum_{\langle ij\rangle} V_{ij} \left(F_{ij}^{\uparrow \downarrow} c_{j\downarrow}^{\dagger}c_{i\uparrow}^{\dagger} +
     F_{ij}^{\uparrow \downarrow\ast} c_{i\uparrow}^{\dagger}c_{j\downarrow}^{\dagger}\right)\\
     =& -\sum_{\langle ij\rangle} V_{ij} \left(F_{ji}^{\uparrow \downarrow} c_{i\downarrow}^{\dagger}c_{j\uparrow}^{\dagger} +
     F_{ij}^{\uparrow \downarrow\ast} c_{i\uparrow}^{\dagger}c_{j\downarrow}^{\dagger}\right)\\
     =& -\frac{1}{2}\sum_{\langle ij\rangle} V_{ij} \left[F_{ij}^{\uparrow \downarrow} \left(c_{i\downarrow}^{\dagger}c_{j\uparrow}^{\dagger} - c_{i\uparrow}^{\dagger}c_{j\downarrow}^{\dagger}\right)
     + F_{ij}^{\uparrow \downarrow\ast}  \left(c_{i\uparrow}^{\dagger}c_{j\downarrow}^{\dagger} - c_{i\downarrow}^{\dagger}c_{j\uparrow}^{\dagger}\right)\right]\\
    \end{aligned}
\end{equation} 
which is achieved using Eq. \ref{eq:Trick1}, $V_{ij} = {V_{ji}}$, $ F_{ij}^{\uparrow \downarrow} = -F_{ji}^{\downarrow \uparrow} = F_{ji}^{\uparrow \downarrow}$
using the anticommutation relation and a spin-echange. We then use $F_{ij}^{\uparrow \downarrow}$ = $F_{ij}$ since all ambiguity has been removed.
Therefore, the matrix we obtain is given as
\begin{equation}\label{eq:H_V_DWave}
    H_{V,ij}^{HF} = -\frac{1}{2}\begin{pmatrix}
        \mathcal{O} & & & -F_{ij}^{\uparrow \downarrow}\\
         & & F_{ij}^{\uparrow \downarrow} & \\
         & F_{ij}^{\uparrow \downarrow\ast}& & \\
         -F_{ij}^{\uparrow \downarrow\ast} & & & \mathcal{O}\\
    \end{pmatrix} = -\frac{1}{2}\begin{pmatrix}
        \mathcal{O} & -\im \sigma_2 F_{ij}\\
        \im \sigma_2 F_{ij}^{\ast} & \mathcal{O}
    \end{pmatrix},
\end{equation}
and takes only place between two neighbouring sites $i$ and $j$. For the accuracy one could multiply it with 
$(\delta_{i+1,j} + \delta_{i-1,j} + \delta_{i+N_x,j} + \delta_{i-N_x,j})$. This matrix can then be added to Eq. \ref{eq:H^_ij} replacing the on-site superconductive $\Delta$-term by
a neighbouring superconductive $F$-term.\\

Now that we have expressed the Hartree-Fock Hamiltonian in the correct manner, we can use our BdG-transformation to diagonalize the Hamiltonian and find a self-consistent solution 
for the $F$-parameters. Here we use the transformation between the creation and annihilation operators, and the eigenvectors, -values of the Hamiltonian given by Eqs. \ref{eq:BdG_transf_c} 
and \ref{eq:BdG_transf_c_dagg}. 
\begin{equation}
    F_{ij} = \langle c_{i\uparrow}c_{j\downarrow}\rangle = \sum_{n\in \mathcal{N}_+} u_{ni\uparrow}v_{nj\downarrow}^{\ast}\left(1 - f(E_{nk})\right) + v_{ni\uparrow}^{\ast}u_{nj\downarrow}f(E_{nk})
\end{equation}
in a very similar way as Eq. \ref{eq:transfo_c_up_c_down_BdG}.


\subsection{Unconventional order parameters}\label{sec:Unconventional_order_parameters}
In the more simple description of the superconductivity we outlied how the superconducting order parameter $\Delta$ depends on the pairing amplitude $F$.
Because the potential was isotropic, we simply had $\Delta = U \langle c_{i\uparrow}c_{i\downarrow}\rangle$. Here however, the potential is anisotropic, 
and we obtain a linear combination of the pairing amplitudes in the different directions of the lattice. Achieving different combinations of the $F$s 
we obtain different superconducting states. Here is an exhaustive list.
\begin{align*}
    \Delta_{s,i} = V F_{s,i} &= \frac{V}{4} \left(F_{i}^{x+(S)} + F_{i}^{x-(S)} + F_{i}^{y+(S)} + F_{i}^{y-(S)}\right)\\
    \Delta_{d,i} = V F_{d,i} &= \frac{V}{4} \left(F_{i}^{x+(S)} + F_{i}^{x-(S)} - F_{i}^{y+(S)} - F_{i}^{y-(S)}\right)\\
    \Delta_{p_x,i} = V F_{p_x,i} &= \frac{V}{2} \left(F_{i}^{x+(T)} - F_{i}^{x-(T)}\right) \\
    \Delta_{p_y,i} = V F_{p_y,i} &= \frac{V}{2} \left(F_{i}^{y+(T)} - F_{i}^{y-(T)}\right)
\end{align*}
$F_s$, $F_d$, $F_{p_x}$ and $F_{p_y}$ are the pairing amplitudes for the $s$, $d$ (also called $d_{x^2-y^2}$ because of its expression), $p_x$ and $p_y$-wave superconductivity.
The $S$ and $T$ are the singlet and triplet expressions of the pairing amplitudes. More precisely we define them as
\begin{align}
    F_{ij}^{(S)} = \frac{F_{ij} + F_{ji}}{2} \\
    F_{ij}^{(T)} = \frac{F_{ij} - F_{ji}}{2}
\end{align}
Where we shorten the expression using $F_{ij}^{\uparrow\downarrow(S)} = F_{ij}^{(S)}$.
\paragraph{Symmetry discussion} $~$\\

We see that these parameters depends on the spin and the momentum. Therefore, it's a good idea to look at their respective
behaviour under exchange of these variables.
The discussion for the spin exchange is quite straight forward.
\begin{align*}
    F_{ij}^{\uparrow\downarrow(S)} =& \frac{F_{ij}^{\uparrow\downarrow} + F_{ji}^{\uparrow\downarrow}}{2} = \frac{\langle c_{i\uparrow}c_{j\downarrow}\rangle + \langle c_{j\uparrow}c_{i\downarrow}\rangle}{2}\\
    F_{ij}^{\uparrow\downarrow(T)} =& \frac{F_{ij}^{\uparrow\downarrow} - F_{ji}^{\uparrow\downarrow}}{2} = \frac{\langle c_{i\uparrow}c_{j\downarrow}\rangle - \langle c_{j\uparrow}c_{i\downarrow}\rangle}{2}
\end{align*}
using $\langle c_{i\uparrow}c_{j\downarrow}\rangle = -\langle c_{i\downarrow}c_{j\uparrow}\rangle$. Using the linearity of the expression we obtain
\begin{align*}
    F_{ij}^{\uparrow\downarrow(S)} = - F_{ij}^{\downarrow\uparrow(S)}\\
    F_{ij}^{\uparrow\downarrow(T)} = F_{ij}^{\downarrow\uparrow(T)}.
\end{align*}
This means that the singlet wave-pairing amplitude is antisymmetric under spin exchange and the triplet wave pairing is symmetric under spin exchange. Their names
find place in the analogy of the wave function formalism.\\

For the momentum exchange we're going to take a look at the Fourier transformation of the pairing amplitudes. Using the transformation we made to 
reach Eq. \ref{eq:transfo_F_x} with any translation $ x \rightarrow \bm{r}$, $r\in \{\bm{e}_x,\bm{e}_y\}$ we obtain
\begin{align*}
    F_{i,i+ \bm{r}} = \frac{1}{N} \sum_{\bm{k}} \langle c_{\bm{k}\uparrow} c_{-\bm{k},\downarrow}\rangle e^{-\im\bm{k}\bm{r}}.
\end{align*}
Changing the sign of the momentum we obtain  $\frac{1}{N} \sum_{\bm{k}} \langle c_{-\bm{k},\uparrow} c_{\bm{k},\downarrow}\rangle e^{\im\bm{k}\bm{r}} =  F_{i,i- \bm{r}}$
because of the $\delta_{\bm{k},\bm{k}'}$ trick. For this reason $F_{i,i+ \bm{r}} +  F_{i,i- \bm{r}}$ is symmetric under momentum exchange while $F_{i,i+ \bm{r}} -  F_{i,i- \bm{r}}$ is antisymmetric.\\
Referring back to the order parameter definition we see that the $s$ and $d$-wave are symmetric under momentum exchange, where the $p_x$ and $p_y$-wave are antisymmetric in such exchange.\\

\subsection{Implementation of the unconventional superconductivity}


This is more complex to implement than the BCS superconductivity. We solved this without the periodic boundary conditions method.
Here each site has to compute eight parameters, the four pairing amplitudes in the $ij$ and $ji$ direction.
To do so we prepare a huge vector containing the eigenvectors' components $u$ and $v$ that all the parameters need and send this to each site.
Further due to computation imprecisions, we may have $F^{(S)}_{ij} \neq F^{(S)}_{ji}$. However, the Hamiltonian
should stay hermitian, so we impose $F^{(S)}_{ij} = F^{(S)}_{ji}$. Please compare the implementation of Eq. \ref{eq:H_V_DWave} in 
the Hamiltonian of the system to check that $H_{ij} = H_{ji}^{\ast}$ is
actually verified. For the convergence criteria it is important to note the following:
The individual $F$ always change but the end result in $F_d$ can converge, so we check $F_{d,i}$ on each step to see if it reaches a stable value.\\
\end{document}  